The hydra and the rooster

### 2020-07-14 latex/chapter-ordinals.tex
Limits_and_Successors now autonomous

>>>>

\begin{Coqsrc}
Definition succ (alpha : t) := match alpha with
                                 inl i => inl (S i)
                               | inr i => inr (S i)
                               end.
\end{Coqsrc}

\begin{Coqsrc}
Lemma Successor_correct alpha beta : Successor beta alpha <-> beta = succ alpha.
\end{Coqsrc}

\begin{Coqsrc}
Definition succb (alpha: t) := match alpha with
                                   inr (S  _) | inl (S _) => true
                                 | _ => false
                                 end.
\end{Coqsrc}

\begin{Coqsrc}
Lemma succb_correct alpha : succb alpha <-> exists beta,  alpha = succ beta.
\end{Coqsrc}

\begin{Coqsrc}
Definition limitb (alpha : t) := match alpha with
                                     (inr 0) => true
                                   | _ => false
                                   end.
\end{Coqsrc}

\begin{Coqsrc}
Lemma omega_is_limit:
   Omega_limit fin omega.
Proof.
  split.
  - constructor.
  - inversion_clear  1.
    + exists (S x); constructor; auto with arith.
    + lia.
Qed.
\end{Coqsrc}
